|

### 2020-09-14 paper.Rmd
try magick

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\\gamma=3$ (bottom)"}
library(cowplot)
library(magick)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_panel <- function(png) ggdraw() + 
  draw_image(png) + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

mex_grand <- paste0(dir, "mouse_grand_2c-", frames, ".png")
mex_grand_panel <- plot_grid(plotlist = lapply(mex_grand, draw_panel), nrow = 1)
mex_sage <- paste0(dir, "mouse_sage_2c_gam3-", frames, ".png")

mex_sage_panel <- plot_grid(plotlist = lapply(mex_sage, draw_panel), nrow = 1)

plot_grid(mex_grand_panel, mex_sage_panel, nrow = 2)
```

@@

sketches_grand <- paste0(dir, "sketches_grand-", frames, ".png")
sketches_grand_panel <- plot_grid(plotlist = lapply(sketches_grand, draw_panel), nrow = 1)
sketches_sage <- paste0(dir, "sketches_sage-", frames, ".png")

sketches_sage_panel <- plot_grid(plotlist = lapply(sketches_sage, draw_panel), nrow = 1)

plot_grid(sketches_grand_panel, sketches_sage_panel, nrow = 2)
```

@@

pdfsense_grand <- paste0(dir, "pdfsense_grand-", frames, ".png")
pdfsense_grand_panel <- plot_grid(plotlist = lapply(pdfsense_grand, draw_panel), nrow = 1)
pdfsense_sage <- paste0(dir, "pdfsense_sage_r10-", frames, ".png")

pdfsense_sage_panel <- plot_grid(plotlist = lapply(pdfsense_sage, draw_panel), nrow = 1)

plot_grid(pdfsense_grand_panel, pdfsense_sage_panel, nrow = 2)
```

>>>>

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\\gamma=3$ (bottom)"}
library(magick)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_frames <- function(pngs) {
  res <- lapply(pngs, image_read)
  res <- do.call("c", res)
  image_append(res)
}

draw_panel <- function(a, b) {
  whitespace <- image_blank(image_info(a)$width, 25, color = "white")
  img <- c(a, whitespace, b)
  image_scale(
    image_append(img, stack = TRUE),
    "800"
  )
}
mouse_grand <- paste0(dir, "mouse_grand_2c-", frames, ".png")
mouse_grand_panel <- draw_frames(mex_grand)
mouse_sage <- paste0(dir, "mouse_sage_2c_gam3-", frames, ".png")
mouse_sage_panel <- draw_frames(mex_sage)

mouse <- draw_panel(mouse_grand_panel, mouse_sage_panel)
print(mouse)
```

@@

sketches_grand <- paste0(dir, "sketches_grand-", frames, ".png")
sketches_grand_panel <- draw_frames(sketches_grand)
sketches_sage <- paste0(dir, "sketches_sage-", frames, ".png")
sketches_sage_panel <- draw_frames(sketches_sage)

sketches <- draw_panel(sketches_grand_panel, sketches_sage_panel)
print(sketches)
```

@@

pdfsense_grand <- paste0(dir, "pdfsense_grand-", frames, ".png")
pdfsense_grand_panel <- draw_frames(pdfsense_grand)
pdfsense_sage <- paste0(dir, "pdfsense_sage_r10-", frames, ".png")
pdfsense_sage_panel <- draw_frames(pdfsense_sage)

pdfsense <- draw_panel(pdfsense_grand_panel, pdfsense_sage_panel)
print(pdfsense)
```
